A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-24 docs/results_JAMwithNFW_v3.02.tex
Legends in three figures; added lensing models in two of them.

%==============
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo. \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
\label{fig:modelB4_vrot}
\end{figure}
%==============

>>>>

%==============
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure}
%==============

### 2015-11-24 docs/results_JAMwithSB_v3.01.tex
Legends in three figures; added lensing models in two of them.

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}. \Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
  \label{fig:JAM_modelL}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}. \Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively. \Wilma{[TO DO: rewrite Caption. Maybe also rewrite text to acknowledge alpha=0.9]}}
  \label{fig:JAM_modelL}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model. \Wilma{[TO DO: Make Line purpel or yellow.]}}
  \label{fig:JAM_modelA2}
\end{figure}
